---
title: "Título do trabalho de conclusão de curso de especialização"
author: "Aluno da Especialização"
role: "Aluno do programa de Especialização em Data Science & Big Data"
email: "email@aluno.com.br"
orientador: "Orientador do Programa"
orientador_role: "Professor do Departamento de Estatística - DEST/UFPR"
ano: "2020"
references: "src/referencias.bib"
biblio-style: unsrt
lang: pt-BR
output:
  bookdown::pdf_document2:
    template: dsbd_tcc.tex
    pandoc_args: ["--natbib"]
resumo: >
  \textit{Lorem Ipsum} is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
palavras_chave: "Lorem, Ipsum, Lorem, Ipsum, Lorem"
abstract: >
  \textit{Lorem Ipsum} is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
keywords: "Lorem, Ipsum, Lorem, Ipsum, Lorem"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
options(knitr.table.format = "latex", scipen = 999)

TABLE_FONT_SIZE <- 9
source("scripts/install.R") # carrega os pacotes necessários, opte por incluir os pacotes adicionais através do script install.R.

theme_set(theme_bw()) # opcional, para uso do ggplot2
```

# Introdução

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

# Materiais e métodos

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

## Subseção de materiais e métodos

```{r metricas}
tb_metricas <- data.frame(Valor = c("0,5", "> 0,5", "< 0,5"),
                     Desempenho= c("Mantido", "Aumentado", "Reduzido"))

kable(tb_metricas, booktabs = T, caption = "Interpretação das métricas de desempenho") %>%
  kable_styling(font_size = TABLE_FONT_SIZE)
```

A tabela \@ref(tab:metricas) indica Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

O objetivo da regressão logística é o estudo da probabilidade de ocorrência de um evento de interesse ($Y$), apresentado na forma dicotômica ($Y=1$ se o evento de interesse ocorrer; $Y=0$, caso contrário), em função de um vetor de covariáveis ($X_1, ..., X_n$). Sua definição ocorre através da equação 
\begin{equation}
\ln \left ( \dfrac{\pi_i}{1-\pi_i} \right ) = \beta_0 + \beta_1 X_{i1} + ... +  \beta_p X_{ip}\text{,}(\#eq:logito)
\end{equation} em que $\beta_j$ ($j = 0,1,2,...,p$) representa os parâmetros a serem estimados, sendo $\beta_0$ o intercepto e os demais, parâmetros de cada covariável. E o subscrito $i$ representa cada observação da amostra ($i = 1, 2,...,n$) \cite{Favero2017}.

A equação \@ref(eq:logito) modela a log-chance de ocorrência do evento de interesse, Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

# Resultados e discussões

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

## Subseção de resultados e discussões

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

```{r grafico, fig.cap='Título do Gráfico', out.width="100%", fig.align='center'}

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point()
```

A figura \@ref(fig:grafico) indica que Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

# Conclusões

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.